Reanalysis Step 5: Outcome Analysis with Three-Way Interaction

### 2025-09-01 reanalysis-5-outcome_analysis-interaction.qmd
logging bug

    # Get marginal means on both log odds and response scales
    emm_logit <- emmeans(models[[i]], 
                         ~ ever_lapse_binary | dr_severity * any_treatment,
                         weights = "proportional")

    emm_response <- emmeans(models[[i]], 
                           ~ ever_lapse_binary | dr_severity * any_treatment,
                           weights = "proportional",
                           type = "response")

@@

    # Get pairwise comparisons on response scale (for risk differences)
    # Use regrid to ensure we get differences not ratios
    risk_diffs <- regrid(emm_response) |>
      pairs(reverse = TRUE, by = c("dr_severity", "any_treatment"))

>>>>

    # Get the data for this imputation (needed for emmeans)
    imp_data <- imputed_datasets[[i]]
    imp_data$weights <- twang_weights[[i]]

    # Get marginal means on both log odds and response scales
    emm_logit <- emmeans(models[[i]], 
                         ~ ever_lapse_binary | dr_severity * any_treatment,
                         weights = "proportional",
                         data = imp_data)

    emm_response <- emmeans(models[[i]], 
                           ~ ever_lapse_binary | dr_severity * any_treatment,
                           weights = "proportional",
                           type = "response",
                           data = imp_data)

@@

    # Get pairwise comparisons on response scale (for risk differences)
    risk_diffs <- pairs(emm_response, reverse = TRUE, 
                       by = c("dr_severity", "any_treatment"))
